\section{Scientific acknowledgements}

I thank prof. dr. Eveline Lescrinier and prof. dr. Mathy Froeyen, my direct supervisors, for always being open to questions and for their guidance in my professional development. I am prof. dr. Piet Herdewijn thankful for bringing up interesting projects and fruitful discussions;  J\'er\^ome Rihon for his assistance in analyzing the puckering \gls{pes} of \gls{cena}; dr. Peter Schofield, dr. Alexander Taylor, Jennifer Jackson, prof. dr. Philipp Holliger and prof. dr. Daniel Christ for their excellent wet-lab work on the \gls{hna} aptamer; Guy Schepers, dr. Munmun Maiti, dr. Mohitosh Maiti, prof. dr. Helmut Rosemeyer for their respective work concerning the \gls{dxyna} and \gls{xyna} oligonucleotides and Laurent Smets for his help analyzing the \gls{nmr} data of the \gls{dxyna} hairpins. Additionally, I would like to express my gratitude to prof. dr. Deirdre Cabooter and prof. dr. Jeroen Lammertyn for their time and guidance as part of my thesis advisory committee and to prof. dr. Hans De Winter and prof. dr. Wim De Borggraeve for being part of the examining committee. Special thanks go to dr. Henri-Philippe Mattelaer for his mentoring (not only scientific), his contributions to \cref{puckering:chap} and \cref{xylo:chap}, the positive discussions about science in general and for helping me through the final year of my PhD. 

Additionally, I am prof. dr. Eveline Lescrinier, prof. dr. Mathy Froeyen, dr. Henri-Philippe Mattelaer and J\'er\^ome Rihon grateful for proofreading this dissertation and a special mention goes to Eva Clerix (medical writer\footnote{also known as ``miracle worker''}) who checked the dissertation for (technical) inconsistencies, spelling, grammar and readability. 

This research was funded by a Strategic Basic research scholarship (1S23217N) by the Research Foundation --- Flanders (FWO).

\section{Personal contributions}

Only personal contributions of submitted and/or published papers directly related to the reported PhD dissertation are described.

\subsubsection{\fullcite{MattelaerCA2020pucker} (\cref{puckering:chap})}

C-A Mattelaer proposed the research goal, conceptualized the methodology and performed all calculations except \gls{cena}. C-A Mattelaer went on to prepare the entire manuscript for publication.

\subsubsection{\fullcite{Schofield2020} (\cref{hna:chap})}

C-A Mattelaer performed the refinement and validation of the \gls{amber} force field for \gls{hna} residues. C-A Mattelaer performed the (accelerated) \gls{md} simulations in order to propose a molecular model for the \gls{hna} aptamer and verify the model's stability. C-A Mattelaer provided the necessary results and discussion to implement in the manuscript.

\subsubsection{\fullcite{MattelaerCA2020dxyna} (\cref{xylo:chap})}

C-A Mattelaer was responsible for the analysis and interpretation of \gls{nmr} spectra, performed \gls{md} simulations, analyzed molecular models and compiled the manuscript.

\section{Conflicts of interest}

The author declares no conflicts of interest or any financial interests.